\chapter{RESEARCH METHODOLOGY}
This chapter of a thesis commences a brief statement and enumerating the main topics that are to be covered in it; namely; (1) Research Design; (2) Sources of Data (Locale of the Study and Population/Sampling); (3) Instrumentation and Data Collection; and (4) Tools for Data Analysis. Writing chapter 3 of a thesis requires the assistance of a statistician (in most cases). This is because it is in this chapter that the thesis writer is usually required to indicate what statistical tools he intends to use in data analysis. Here is the basic format of Chapter 3. 

% =========================================================
\section{Research Design}
% =========================================================
The appropriate research design should be specified and described (including requirement, modeling and detailed description of system/product/method development.
\subsection{System/product/method Implementation}
Describe the place where the study was conducted and the rationale behind its choice, the environment of the system (device specification, tools specification and language, which were used in the implementation)
\subsection{Experiment Scenario}
Describe the experiment scenario (including the objective, the procedure of the experiment and the variable which will be used in the experiment).
\subsubsection{This is a subsubsection}
\subsubsubsection{This is a subsubsubsection}

% =========================================================
\section{Population/Sampling}
% =========================================================
Describe the population of interest and the sampling of subjects used in the study.

% =========================================================
\section{Instrumentation and Data Collection}
% =========================================================
Describe the instrument, what it will measure, how to interpret. Discuss how the validity and the reliability will be established. Specify the level of reliability (probability). Give details of instruction given to assistants if persons other than the researcher gather data. State qualifications of informants if used in the study.

% =========================================================
\section{Tools for Data Analysis}
% =========================================================
Determine and justify the statistical treatment for each sub-problem, the scales of values used and the descriptive equivalent ratings, if any.
